---
title: "Quarto Demo"
author: "MDA Team"
date: "2023-10-19"
format: gfm
---


Before you render this file with `quarto`, you will need to make sure that
the [`quarto cli`](https://quarto.org/docs/get-started/) *and* the following `R` packages are available in your local
environment (shell/terminal)...
```{r}
## Initial setup ----
#| output: false
#| warning: false
suppressMessages({
    if (!require("tidyverse") || !require("palmerpenguins")) {
        options(
         repos = c(CRAN = "https://cran.rstudio.com")
        )
        install.packages(c(
            "tidyverse",
            "palmerpenguins"
            )
        )
    }
})
```

Once this dependency is satisfied, render this README with this command:
```
quarto render README.qmd --cache-refresh  --verbose`
```

# First section

## First slide

Table below shows the first six rows from the MTCars dataset
```{r}
head(mtcars)
```

## Second slide

@fig-mtscatter shows a relationship between `wt` and `mpg` features in the MTCars dataset.
```{r}
#| label: fig-mtscatter
#| fig-cap: Weight of vehicle per 1000lbs (wt) vs. Miles/Gallon (mpg)

library(ggplot2)

ggplot(mtcars, aes(x = wt, y = mpg)) +
    geom_point(color = "#0099f9", size = 5)
```
