---
title: "Quarto Demo"
author: "MDA Team"
date: "2023-10-19"
format:
  gfm:
    filters:
    - gfm-strip-disallowed
---


Before you render this file with `quarto`, you will need to make sure that the [`quarto cli`](https://quarto.org/docs/get-started/) *and* the following `R` packages are available in your local environment (shell/terminal):

```{r, echo=TRUE}
required_packages <- c(
  "markdown",
  "tidyverse",
  "palmerpenguins"
)
```

```{r}
## Initial setup ----
#| echo: false
#| output: false
#| warning: false

suppressMessages({
    if (!require("tidyverse") || !require("palmerpenguins")) {
        options(
         repos = c(CRAN = "https://cran.rstudio.com")
        )
        install.packages(required_packages)
    }
})
```

Once this dependency is satisfied, render this README (as markdown) with this command:

    quarto render README.qmd --cache-refresh --output README.md --to gfm  --verbose

Render the entire project with this `npm` command:

    npm run build:all

Render the entire project as markdown with this `npm` command:

    npm run build:markdown

